---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ExactCIone
<!-- badges: start --> 
An R package to construct the admissible exact intervals for the binomial proportion, the poisson mean and the total number of subjects with a certain attribute or the total number of the subjects for the hypergeometric distribution. Both one-sided and two-sided intervals are of interest. This package can be used to calculate the intervals constructed methods developed by Wang (2014) and Wang (2015).
<!-- badges: end -->

## Installation
You can install the development version of ExactCIone like so:
``` r
library("devtools")
install_github("befrthunder/ExactCIone")

```

## Example
This is a basic example which shows you how to solve a common problem:
```{r example}
library(ExactCIone)
# For bin(n,p), construct the CI for p on the observed sample x.
WbinoCI(x=2,n=5,conf.level=0.95,details=TRUE)
WbinoCI(x=2,n=5,conf.level=0.95)
WbinoCI_lower(x=2,n=5,conf.level=0.95,details=TRUE)
WbinoCI_lower(x=2,n=5,conf.level=0.95)
########################################################################
# For pois(lambda), construct the CI for lambda on the observed sample x.
WpoisCI(x=3,details = TRUE)
WpoisCI(x=1)
WpoisCI_lower(x=1)
WpoisCI_lower(x=3,details = TRUE)
WpoisCI_upper(x=1)
WpoisCI_upper(x=3,details = TRUE)
#######################################################################
# For hyper(n,x,M,N-M), construct the CI for N on the observed sample x when n,M are known.
WhyperCI_N(10,50,800,0.95,details=TRUE)
WhyperCI_N(50,50,800,0.95)
WhyperCI_N_lower(0,50,800,0.95,details=TRUE)
WhyperCI_N_lower(0,50,800,0.95)
WhyperCI_N_upper(0,50,800,0.95,details=TRUE)
WhyperCI_N_upper(0,50,800,0.95)
#######################################################################
# For hyper(n,x,M,N-M), construct the CI for M on the observed sample x when n, N are known.
WhyperCI_M(0,50,2000,0.95,details = TRUE)
WhyperCI_M(0,50,2000,0.95)
WhyperCI_M_lower(0,50,2000,0.95,details = TRUE)
WhyperCI_M_lower(0,50,2000,0.95)
WhyperCI_M_upper(0,50,2000,0.95,details = TRUE)
WhyperCI_M_upper(0,50,2000,0.95)
## basic example code
```
