---
title: "Vignette for the R package ExactCIone"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ExactCIone_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

## Introduction
An R package to construct the admissible exact confidence intervals (CI) for the binomial proportion, the poisson mean and the total number of subjects with a certain attribute or the total number of the subjects for the hypergeometric distribution. Both one-sided and two-sided CI are of interest. This package can be used to calculate the intervals constructed methods developed by Wang (2014) and Wang (2015).



## Admissible exact CI for binomial proportion 
Suppose $X\sim bino(n,p)$, the sample space of $X$ is $\{0,1,...,n\}$. Wang
(2014) proposed an admissible interval for $p$ which is obtained by uniformly shrinking the initial $1-\alpha$ Clopper-Pearson interval from the middle to both sides of the sample space iteratively. This interval is admissible so that any proper sub-interval of it cannot assure the confidence coefficient. So the interval cannot be shortened anymore.


```{r setup}
library(ExactCIone)
```
```{r}
# Compute the 95% confidence interval when x=2, n=5.
WbinoCI(x=2,n=5,conf.level=0.95)
```
Use "details=TRUE" to show the CIs of the whole sample space.
```{r}
WbinoCI(x=2,n=5,conf.level=0.95,details=TRUE)
```
The one-sided intervals are the one-sided $1-\alpha$ Clopper-Pearson intervals (Clopper and Pearson, 1934). Also shows all the CIs when "details=TRUE".
```{r}
WbinoCI_lower(x=2,n=5,conf.level=0.95)
WbinoCI_lower(x=2,n=5,conf.level=0.95,details=TRUE)
WbinoCI_upper(x=2,n=5,conf.level=0.95)
WbinoCI_upper(x=2,n=5,conf.level=0.95,details=TRUE)
```


## Admissible exact CI for the poisson mean $\lambda$
Suppose $X\sim poi(\lambda)$, the sample space of $X$ is $\{0,1,...\}$. Wang (2014) proposed an admissible interval for $\lambda$ which is obtained by uniformly shrinking the initial $1-\alpha$ Clopper-Pearson interval one by one from 0 to the sample point of interest. This interval is admissible so that any proper sub-interval of it cannot assure the confidence coefficient, which means the interval cannot be shortened anymore.

```{r}
# The admissible CI for poisson mean when the sample observed is x=3. 
WpoisCI(x=1)
#We show the intervals from 0 to the sample of interest when "details=TRUE".
WpoisCI(x=3,details = TRUE)
```
The one-sided intervals are the one-sided $1-\alpha$ Clopper-Pearson intervals which is givend by Garwood (1936). Also shows all the CIs when "details=TRUE".
```{r}
WpoisCI_lower(x=1)
WpoisCI_lower(x=3,details = TRUE)
WpoisCI_upper(x=1)
WpoisCI_upper(x=3,details = TRUE)
```


## Admissible exact confidence intervals for N, the number of balls in an urn.
Suppose $X\sim Hyper(M,N,n)$. The sample space is $\{0,\ldots,\min(M,n)\}$. When $M$ and $n$ are known, Wang (2015) construct an admissible confidence interval for $N$ by uniformly shrinking the initial $1-\alpha$ Clopper-Pearson type interval from  0 to $\min(M,n)$. Also this interval cannot be shortened more.
```{r}
# For hyper(M,N,n), construct 95% CI for N on the observed sample x when n,M are known.
WhyperCI_N(x=50,n=50,M=800,0.95)
# It shows CIs for all the sample point When "details=TRUE".
WhyperCI_N(x=10,n=50,M=800,0.95,details=TRUE)
```

The one-sided $1-\alpha$ CI for $N$ is the one-sided Clopper-Pearson type interval (Konijn, 1973).
```{r}
WhyperCI_N_lower(x=0,n=50,M=800,0.95)
WhyperCI_N_lower(x=0,n=50,M=800,0.95,details=TRUE)
WhyperCI_N_upper(x=0,n=50,M=800,0.95)
WhyperCI_N_upper(x=0,n=50,M=800,0.95,details=TRUE)
```


## Admissible exact CI for $M$, the number of white balls in an urn
Suppose $X\sim Hyper(M,N,n)$. When N and n are known, Wang (2015) construct an admissible confidence interval for N by uniformly shrinking the initial $1-\alpha$ Clopper-Pearson type interval from  the mid-point of the sample space to 0. This interval is admissible so that any proper sub-interval of it cannot assure the confidence coefficient. This means the interval cannot be shortened anymore.
```{R}
# For Hyper(M,N,n), construct the CI for M on the observed sample x 
# when n, N are known. 
# Also output CI for p=M/N.
WhyperCI_M(x=0,n=50,N=2000,0.95)
WhyperCI_M(x=0,n=50,N=2000,0.95,details = TRUE)
```
The one-sided $1-\alpha$ CI for $M$ is the one-sided Clopper-Pearson type interval (Konijn, 1973).
```{R}
WhyperCI_M_lower(X=0,n=50,N=2000,0.95)
WhyperCI_M_lower(X=0,n=50,N=2000,0.95,details = TRUE)
WhyperCI_M_upper(X=0,n=50,N=2000,0.95)
WhyperCI_M_upper(X=0,n=50,N=2000,0.95,details = TRUE)

```
